---
title: "Elasticities between Regions"
author: "Phillip Riehle"
date: "1 9 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preface 

In this part we load and install if necessary all neded packages to run the file

```{r Preface, message=FALSE, warning=FALSE, paged.print=FALSE}

rm(list = ls())

libraries = c("openxlsx", "data.table", "dplyr", "ggplot2", "reshape", "officer", "magrittr", "flextable", "readxl", "tidyr", "stringr", "keyring", "knitr", "eurostat", "tidyverse","rvest","Rcpp","jtools","magrittr","utils","ggpubr")

lapply(libraries, function(x) if (!(x %in% installed.packages())) {
  install.packages(x)
})
lapply(libraries, library, quietly = TRUE, character.only = TRUE)

```

# Data Download

Since the data we need for our regression analysis is only available via a .xlsx file publicly available on the web we need to download the file. This part of the file seeks to do so. 

```{r Data Download}
# First we need to define the loaction of the data and the file in wich we want to safe it

dwnl_data <- list() 
dwnl_data$url[1] <- c("https://www.statistikportal.de/sites/default/files/2021-03/vgrdl_r1b1_bs2020.xlsx")

# ATENTION: PLEASE CHANGE THE DATA LOCATION TO YOUR WORKING DIRECTORY

dwnl_data$dest[1] <- c("C:/Users/phill/Dropbox/Student_Tom/ENTRANCES_Phillip/Elast_Regions_Energy/Data/VGR_DE.xlsx")

# To avoid multiple downloads check if the file does already exists

if (!file.exists(dwnl_data$dest[1])){
  
  download.file(dwnl_data$url[1], method = "auto",destfile  =dwnl_data$dest[1] , mode = "wb")
  
} else {
  
  print("The file does already exists and is not downloaded again")
  
}


```

# Data Transformation 

This part reads the previously downloaded file and transforms and manipulate the data to fit to our regression analysis

## Define Filters 

In Order to more easyly  extract the data we initialize a filter list which will be used in the following extraction function

```{r Data Transformation: Define Filters}

# We define a filter list to extract the necessary data from the xlsx file

var_filter <- list()

# GVA_D_NUTS1
var_filter$name[[1]]          <- c("GVA_D_NUTS1")
var_filter$sheet_name[[1]]    <- c("2.3.1.3")
var_filter$rows[[1]]          <- c(2,5:15)
var_filter$columns[[1]]       <- c(1:18) 

# GVA_B_NUTS1
var_filter$name[[2]]          <- c("GVA_B_NUTS1")
var_filter$sheet_name[[2]]    <- c("2.3.1.1")
var_filter$rows[[2]]          <- c(2,5:15)
var_filter$columns[[2]]       <- c(1:18) 

# GVA_TOTAL_NUTS1
var_filter$name[[3]]          <- c("GVA_TOTAL_NUTS1")
var_filter$sheet_name[[3]]    <- c("2.1")
var_filter$rows[[3]]          <- c(2,5:34)
var_filter$columns[[3]]       <- c(1:18) 

# GVA_D_r_Index_NUTS1
var_filter$name[[4]]          <- c("GVA_D_r_Index_NUTS1")
var_filter$sheet_name[[4]]    <- c("7.3.1.3")
var_filter$rows[[4]]          <- c(2,16:26)
var_filter$columns[[4]]       <- c(1:18) 

# GVA_B_r_Index_NUTS1
var_filter$name[[5]]          <- c("GVA_B_r_Index_NUTS1")
var_filter$sheet_name[[5]]    <- c("7.3.1.1")
var_filter$rows[[5]]          <- c(2,16:26)
var_filter$columns[[5]]       <- c(1:18) 

# GVA_TOTAL_r_Index_NUTS1
var_filter$name[[6]]          <- c("GVA_TOTAL_r_Index_NUTS1")
var_filter$sheet_name[[6]]    <- c("7.3")
var_filter$rows[[6]]          <- c(2,36:64)
var_filter$columns[[6]]       <- c(1:18) 

```

## Data Extraction 

Here we extract the data 

```{r Data Transformation: Data Extraction, message=FALSE, warning=FALSE, echo = TRUE}

# Define a variable list

var_list <- list() # empty list

for (iVar in 1:length(var_filter$name)){
  
  temp              <- read_excel(dwnl_data$dest[1], sheet = var_filter$sheet_name[[iVar]]) 
  temp              <- temp[var_filter$rows[[iVar]],var_filter$columns[[iVar]]]
  names(temp)       <- as.character(temp[1,])
  temp              <- temp[-1,] %>% as.data.frame()
  
  var_list[[as.character(var_filter$name[iVar])]]             <- data.frame(t(temp[-1]))
  colnames(var_list[[as.character(var_filter$name[iVar])]])   <- temp[, 1]
  
  var_list[[as.character(var_filter$name[iVar])]]             <- tibble::rownames_to_column(var_list[[as.character(var_filter$name[iVar])]] , "NUTS1")
  
}
```
## Data to one dataframe: 

```{r Data Transformation: Data Frame}

data_trans <- function(data_fram) {

  df_temp <- data.frame()
  
  for (iReg in 1:nrow(data_fram)){
  
    temp <- data.frame(t(data_fram[iReg,]))
    df <- data.frame()
    for (icount in 1:nrow(temp)){
  
      df[icount,1] <- as.character(temp[1,1])
      df[icount,2] <- row.names(temp)[icount]
      df[icount,3] <- temp[icount,1]
      df_b <- df[-1,]
      }
    df_temp <- rbind(df_temp,df_b)
  }
  return(df_temp)
}

df_list <- list()

for (ivar in 1:length(var_list)){
  
  df_list[[paste("df",names(var_list[ivar]),sep = "_")]] <- data_trans(var_list[[ivar]])
  colnames(df_list[[paste("df",names(var_list[ivar]),sep = "_")]]) <- c("NUTS1", "Year", var_filter$name[ivar])
}
```

## Merge the dataframes

```{r Data Transformation: Merge, message=FALSE, warning=FALSE}

df_final <- Reduce(function(...) merge(..., by= c("NUTS1", "Year"), all.x=TRUE), df_list)

# convert the data to numeric

df_final[, c(3:8)] <- as.numeric(unlist(df_final[, c(3:8)]))

show(kable(head(df_final)))
```
## Data Calculations:

Here we calculate the Index of the GVA in nominal terms. Furthermore we calculate the price index for both sectors 

```{r Data Transformation: Data Calculations (Price Index)}

# GVA Index nominal terms

for (iNUTS in 1:length(df_final$GVA_D_NUTS1)){
  
  df_final$GVA_D_Index[iNUTS]       <- df_final$GVA_D_NUTS1[iNUTS]/ df_final$GVA_D_NUTS1[df_final$Year == c("2015") & df_final$NUTS1 == df_final$NUTS1[iNUTS]]
  
  df_final$GVA_B_Index[iNUTS]       <- df_final$GVA_B_NUTS1[iNUTS]/ df_final$GVA_B_NUTS1[df_final$Year == c("2015") & df_final$NUTS1 == df_final$NUTS1[iNUTS]]
  
  df_final$GVA_D_r[iNUTS]               <- df_final$GVA_D_r_Index[iNUTS]/100 * df_final$GVA_D_NUTS1[df_final$Year == 2015 & df_final$NUTS1 == df_final$NUTS1[iNUTS]]
  
  df_final$GVA_TOTAL_r[iNUTS]           <- df_final$GVA_TOTAL_r_Index[iNUTS]/100 * df_final$GVA_TOTAL_NUTS1[df_final$Year == 2015 & df_final$NUTS1 == df_final$NUTS1[iNUTS]]

}
# NE Calculations

df_final$GVA_NE_NUTS1       <- df_final$GVA_TOTAL_NUTS1 - df_final$GVA_D_NUTS1
df_final$GVA_NE_r_NUTS1     <- df_final$GVA_TOTAL_r - df_final$GVA_D_r

# GVA Price Index

df_final$P_D_NUTS1      <- df_final$GVA_D_Index/(df_final$GVA_D_r_Index/100) 
df_final$P_B_NUTS1      <- df_final$GVA_B_Index/(df_final$GVA_B_r_Index/100) 
df_final$P_NE_NUTS1     <- df_final$GVA_NE_NUTS1/(df_final$GVA_NE_r_NUTS1)
```

Now we extract the data for the NUTS 0 Region and allocate it to the NUTS 1 Regions


```{r Data Transformation: NUTS 0 Regions}

# extract the data for the NUTS 0 Region

df_NUTS0 <- df_final[c(56:66),] 

# Delete the data from the data frame 
df_final <- df_final[-c(56:66),]

# Allocate the data to the data frame

for (iNUTS in 1:length(df_final$NUTS1)){

  df_final$GVA_D_NUTS0[iNUTS]         <- df_NUTS0$GVA_D_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]] 
  df_final$GVA_B_NUTS0[iNUTS]         <- df_NUTS0$GVA_B_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]]
  df_final$GVA_NE_NUTS0[iNUTS]        <- df_NUTS0$GVA_NE_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]]
  df_final$GVA_TOTAL_NUTS0[iNUTS]     <- df_NUTS0$GVA_TOTAL_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]]
  
  df_final$P_D_NUTS0[iNUTS]           <- df_NUTS0$P_D_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]]
  df_final$P_B_NUTS0[iNUTS]           <- df_NUTS0$P_B_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]]
  df_final$P_NE_NUTS0[iNUTS]          <- df_NUTS0$P_NE_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]]
  df_final$P_TOTAL_NUTS0[iNUTS]       <- df_NUTS0$P_TOTAL_NUTS1[df_NUTS0$Year == df_final$Year[iNUTS]]
  
  }

```

Now we calculate the growth rates

```{r Data Transformation: Data Calculations (Growth rates)}

# calculate the shares

df_final$GVA_D_Share    <- df_final$GVA_D_NUTS1/df_final$GVA_D_NUTS0
df_final$GVA_B_Share    <- df_final$GVA_B_NUTS1/df_final$GVA_B_NUTS0
df_final$GVA_NE_Share   <- df_final$GVA_NE_NUTS1/df_final$GVA_NE_NUTS0

# calculate the growth rates 
for (iNUTS in 2:length(df_final$NUTS1)){
  
  temp_D    <- (df_final$GVA_D_Share[[iNUTS]]/ df_final$GVA_D_Share[[iNUTS-1]])-1
  temp_B    <- (df_final$GVA_B_Share[[iNUTS]]/ df_final$GVA_B_Share[[iNUTS-1]])-1
  temp_NE   <- (df_final$GVA_NE_Share[[iNUTS]]/ df_final$GVA_NE_Share[[iNUTS-1]])-1
  
  temp_pi_D_NUTS0     <- ((df_final$P_D_NUTS0[[iNUTS]]/(df_final$P_D_NUTS0[[iNUTS-1]])))-1
  temp_pi_B_NUTS0     <- ((df_final$P_B_NUTS0[[iNUTS]]/(df_final$P_B_NUTS0[[iNUTS-1]])))-1
  temp_pi_NE_NUTS0    <- ((df_final$P_NE_NUTS0[[iNUTS]]/(df_final$P_NE_NUTS0[[iNUTS-1]])))-1
  
  
  temp_pi_D_NUTS1     <- ((df_final$P_D_NUTS1[[iNUTS]]/(df_final$P_D_NUTS1[[iNUTS-1]])))-1
  temp_pi_B_NUTS1     <- (df_final$P_B_NUTS1[[iNUTS]]/(df_final$P_D_NUTS1[[iNUTS-1]]))-1
  temp_pi_NE_NUTS1    <- (df_final$P_NE_NUTS1[[iNUTS]]/(df_final$P_NE_NUTS1[[iNUTS-1]]))-1
  
  
  # Only calculate growth rates if we are in the same region
  if (df_final$NUTS1[iNUTS] == df_final$NUTS1[iNUTS-1]){
    df_final$gr_gva_D_share[iNUTS]    <- temp_D
    df_final$gr_gva_B_share[iNUTS]    <- temp_B
    df_final$gr_gva_NE_share[iNUTS]   <- temp_NE
    
    df_final$pi_D_NUTS0[iNUTS]    <- temp_pi_D_NUTS0
    df_final$pi_B_NUTS0[iNUTS]    <- temp_pi_B_NUTS0
    df_final$pi_NE_NUTS0[iNUTS]   <- temp_pi_NE_NUTS0
    
    
    df_final$pi_D_NUTS1[iNUTS]    <- temp_pi_D_NUTS1
    df_final$pi_B_NUTS1[iNUTS]    <- temp_pi_B_NUTS1
    df_final$pi_NE_NUTS1[iNUTS]   <- temp_pi_NE_NUTS1
    
  }
  else {
    df_final$gr_gva_D_share[iNUTS] <- NA
    df_final$gr_gva_B_share[iNUTS] <- NA
    df_final$gr_gva_NE_share[iNUTS] <- NA
  
    df_final$pi_D_NUTS0[iNUTS]    <- NA
    df_final$pi_B_NUTS0[iNUTS]    <- NA
    df_final$pi_NE_NUTS0[iNUTS]   <- NA
  
    df_final$pi_B_NUTS1[iNUTS]    <- NA
    df_final$pi_D_NUTS1[iNUTS]    <- NA
    df_final$pi_NE_NUTS1[iNUTS]   <- NA
  } 
}
```

# Data Visualisation

Here we visulize the previous generated dataset


```{r Data Visualisation }

NUTS1 <- unique(df_final$NUTS1)

# Plot for Gross Value Added Shares for all Regions

GVA_D_Share_Plot    <- list()
GVA_B_Share_Plot    <- list()
GVA_NE_Share_Plot   <- list()

for (iReg in 1:length(NUTS1)){
  
  dfpart <- subset(df_final, NUTS1 == c(NUTS1[iReg]))
  
  GVA_D_Share_Plot[[iReg]] <- ggplot(dfpart, aes(x=as.integer(Year))) +
    geom_line(aes(y=GVA_D_Share), color = "black") +
      labs(title=paste(c("Gross Value Added Share Energy"), c(NUTS1[iReg])), 
       caption="Source: DESTATIS", 
       y="GVA D Share", x= "Year")
  
  GVA_B_Share_Plot[[iReg]] <- ggplot(dfpart, aes(x=as.integer(Year))) +
    geom_line(aes(y=GVA_B_Share), color = "black") +
      labs(title=paste(c("Gross Value Added Share Mining"), c(NUTS1[iReg])), 
       caption="Source: DESTATIS", 
       y="GVA B Share", x= "Year")
  
  GVA_NE_Share_Plot[[iReg]] <- ggplot(dfpart, aes(x=as.integer(Year))) +
    geom_line(aes(y=GVA_NE_Share), color = "black") +
      labs(title=paste(c("Gross Value Added Share Non Energy"), c(NUTS1[iReg])), 
       caption="Source: DESTATIS", 
       y="GVA NE Share", x= "Year")
  
  GVA_B_Share_Plot[[iReg]]
    show(ggarrange(GVA_D_Share_Plot[[iReg]], GVA_NE_Share_Plot[[iReg]], ... =  GVA_B_Share_Plot[[iReg]], 
          ncol = 1, nrow = 3))
}
```
# Regression Part

```{r Regression Part}
reg <- list()

# Elasticity Energy between Regions
reg$reg_D     <- lm(data = df_final, gr_gva_D_share ~ pi_D_NUTS0 + pi_D_NUTS1)

reg$reg_B     <- lm(data = df_final, gr_gva_B_share ~ pi_B_NUTS0 + pi_B_NUTS1)

reg$reg_NE    <- lm(data = df_final, gr_gva_NE_share ~ pi_NE_NUTS0 + pi_NE_NUTS1)

for (ireg in 1:length(reg)){
  
  show(summ(reg[[ireg]]))
  plot(reg[[ireg]][["residuals"]])
  abline(reg[ireg])
}

```

## Parameter Calculation

```{r Parameter Calculation}

eta <- list()
eta$D   <- 1 - reg$reg_D$coefficients[3]
eta$B   <- 1 - reg$reg_B$coefficients[3]
eta$NE  <- 1 - reg$reg_NE$coefficients[3]

show(eta)



```

