---
title: "Estimation_Elast_Sectors"
author: "Phillip Riehle"
date: "26 8 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preface

In this part we load and install (if not already) the needed packages for this file

```{r, warnings = FALSE, error = FALSE, message= FALSE, results = 'hide'}
# Load necessary libraries
rm(list = ls())
libraries = c("eurostat","rvest", "knitr", "tidyverse", "Rcpp", "jtools", "ggplot2","ggpubr", "usefun","data.table", "dplyr","reshape", "officer", "magrittr", "flextable", "readxl", "tidyr", "stringr", "keyring")

lapply(libraries, function(x) if (!(x %in% installed.packages())) {
  install.packages(x)
})
lapply(libraries, library, quietly = TRUE, character.only = TRUE)

## settings for ggplot2
theme_set(theme_classic())
```

# Data Function Part

Here we define the function to download the needed data set from EUROSTAT. Therefore we use the previous loadeded package “eurostat”

```{r}
generate_dataset_csec_elast <- function(country){
  # In the first part we search for the right dataset on the EUROSTAT website
  id    <- c("nama_10_a64")  
  
  # Now we download the full dataset for the defined id
  dum   <- get_eurostat(id, time_format = "num")
  
  # Extract from the data set the information you want (by manual search)

  df    <- subset(dum, unit %in% c("CP_MNAC", "PD15_NAC") & nace_r2 %in% c("TOTAL", "B", "D")& na_item == "B1G" & time %in% 1991:2019)
  
  # Create the data set for the country you are interested in
  df    <- subset(df, geo== country)
  
  # Change the "design" of the data set to fit to the regression model 
  df    <- df %>%
    pivot_wider(names_from = c("nace_r2", "unit"), values_from = values) %>%
    
    rename(c("na_item" = "var", "geo" = "country" , "time" = "year","B_CP_MNAC" = "gva_b", "D_CP_MNAC" = "gva_d", "TOTAL_CP_MNAC" = "gva_total", "B_PD15_NAC" = "p_b", "D_PD15_NAC" = "p_d", "TOTAL_PD15_NAC" = "p_total")) 
  
  # rearrange columns
  df    <- df[, c(2,3,6,4,5,9,7,8)] 
  # change the order
  df    <- df[order(df$year),]
  
  # Calculations
  df$p_bd                   <- (unlist(df$p_b)+unlist(df$p_d))/2
  df$gva_bd_share           <- (unlist(df$gva_b) + unlist(df$gva_d))/unlist(df$gva_total)
  df$g_gva_bd_share         <- unlist(df$gva_bd_share)/unlist(lag(df$gva_bd_share),1) 
  df$dp                     <- unlist(df$p_total)/unlist(lag(df$p_total),1)
  df$dp_bd                  <- unlist(df$p_bd)/unlist(lag(df$p_bd),1)
  
  # Retrun the output
  return(df)
}
```

For the further analysis we define a set of countries here and generate the data set.

*CHANGE COUNTRIES HERE*

```{r}
country_list    <- c("DE", "PL", "RO", "SK", "IT") # all coal countries in the ENTRANCES Project
```

Load the data set for the defined country list

```{r, warnings = FALSE, error = FALSE, message= FALSE, results = 'hide'}
# Generate the dataset
df_final <- NULL
for (i in 1:length(country_list)){
  temp    <- generate_dataset_csec_elast(country_list[i])
  df_final      <- rbind(df_final, temp)
}
```

# Data Inspection and Visualisation {.tabset}


## Inspection

```{r}
kable(head(df_final),"pipe")
```

## Plot (Real Gross Value Added)

```{r}
gva_total_plot      <- list()
gva_b_plot          <- list()
gva_d_plot          <- list()

for (icountry in 1:length(country_list)){
  dfpart <- subset(df_final, country == c(country_list[icountry]))
  
  gva_total_plot[[c(country_list[icountry])]] <- ggplot(dfpart, aes(x=year)) + 
  geom_line(aes(y=gva_total/p_total), color = "red") + 
  labs(title=paste(c("Real Gross Value Added"), c(country_list[icountry])), 
       caption="Source: EUROSTAT", 
       y="Real GVA ")

  gva_b_plot[[c(country_list[icountry])]] <- ggplot(dfpart, aes(x=year)) + 
  geom_line(aes(y=gva_b/p_b), color = "green") + 
  labs(title=paste(c("Real Gross Value Added Mining Sector"), c(country_list[icountry])), 
       caption="Source: EUROSTAT", 
       y="Real GVA")

  gva_d_plot[[c(country_list[icountry])]] <- ggplot(dfpart, aes(x=year)) + 
  geom_line(aes(y=gva_d/p_d), color = "blue") + 
  labs(title=paste(c("Real Gross Value Added Energy Sector"), c(country_list[icountry])), 
       caption="Source: EUROSTAT", 
       y="Real GVA")

  show(ggarrange(gva_total_plot[[c(country_list[icountry])]], gva_b_plot[[c(country_list[icountry])]], ... =  gva_d_plot[[c(country_list[icountry])]], 
          ncol = 1, nrow = 3))
}
```

## Plot (Gross Value Added Share)

```{r}
gva_share_plot <- list()

for (icountry in 1:length(country_list)){
  dfpart <- subset(df_final, country == c(country_list[icountry]))
  gva_share_plot[[c(country_list[icountry])]] <- ggplot(dfpart, aes(x = year)) +
    geom_line(aes(y=gva_bd_share), color = "black") + 
    labs(title=paste(c("Gross Value Added Share for Energy + Mining"), c(country_list[icountry])), 
       caption="Source: EUROSTAT", 
       y="GVA Share")
  show(gva_share_plot[[icountry]])
}  
```

# Regression Part {.tabset}

We want to test the following equation: \(Y_{r,k,t} = \omega^{c}_k * (\frac{P_{r,k,t}}{P_{r,t}})^{\eta^{c}} * Y_{r,t}\)

Now we do some basic rearranging

\(\;Y_{r,k,t} = \omega^{c}_k * (\frac{P_{r,k,t}}{P_{r,t}})^{\eta^{c}} * Y_{r,t}\; |:Y_{r,t}\)

\(\Leftrightarrow \frac{Y_{r,k,t}}{Y_{r,t}} = \omega^{c}_k * (\frac{P_{r,k,t}}{P_{r,t}})^{\eta^{c}} \;|*\frac{P_{r,k,t}}{P_{r,t}}\)

\(\Leftrightarrow \frac{Y_{r,k,t}*P_{r,k,t}}{Y_{r,t}*P_{r,t}} = \omega^{c}_k * (\frac{P_{r,k,t}}{P_{r,t}})^{(1-\eta^{c})} \;|\frac{Y_{r,k,t}*P_{r,k,t}}{Y_{r,t}*P_{r,t}} = \Omega^{energy}_{t}\textrm{: gross value added share of energy}\)

\(\Leftrightarrow\Omega^{energy}_{t} = \omega^{c}_k * (\frac{P_{r,k,t}}{P_{r,t}})^{(1-\eta^{c})} \;| : \Omega^{energy}_{t-1}\)

\(\Leftrightarrow\frac{\Omega^{energy}_{t}}{\Omega^{energy}_{t-1}} = \frac{\omega^{c}_k}{\omega^{c}_k} * (\frac{(\frac{P_{r,k,t}}{P_{r,t}})}{(\frac{P_{r,k,t-1}}{P_{r,t-1}})})^{(1-\eta^{c})} \;| \textrm{rearrange}\)

\(\Leftrightarrow\frac{\Omega^{energy}_{t}}{\Omega^{energy}_{t-1}} = [(\frac{P_{r,k,t}}{P_{r,k,t-1}})/(\frac{P_{r,t}}{P_{r,t-1}})]^{(1-\eta^{c})} \;|\textrm{log}\)

\(\Leftrightarrow\log(\frac{\Omega^{energy}_{t}}{\Omega^{energy}_{t-1}}) = (1-\eta^{c}) \log[(\frac{P_{r,k,t}}{P_{r,k,t-1}})/(\frac{P_{r,t-1}}{P_{r,t}})]\;|\log(\frac{P_{r,k,t}}{P_{r,k,t-1}}) = \pi_{r,k,t},\: \log(\frac{P_{r,t}}{P_{r,t-1}})=\pi_{r,t}\)

\(\Leftrightarrow\log(\frac{\Omega^{energy}_{t}}{\Omega^{energy}_{t-1}}) = (1-\eta^{c})(\pi_{r,k,t}-\pi_{r,t})\)


## Create dummies

```{r}
for (icountry in 1:length(country_list)){
  df_final[[(country_list[icountry])]]  <- NA    

  for(row in 1:length(df_final$country)){
  if (df_final$country[row] == country_list[icountry]) {df_final[(country_list[icountry])][row,] = as.numeric(1)} 
  else {df_final[(country_list[icountry])][row,] = 0 }
  }
}  
# convert logical expressions to numeric: 
cols <- sapply(df_final, is.logical)
df_final[,cols] <- lapply(df_final[,cols], as.numeric)
kable(head(df_final[,14:18]))
```

## Model 1

```{r}
model1_list <- list()

for (icountry in 1:length(country_list)){
  
  pi_r_k_t_minus_pi_r_t <- unlist(I(df_final[(country_list[icountry])]*(log(df_final$dp_bd)-log(df_final$dp))))
  reg1                  <- lm(data = df_final,log(g_gva_bd_share) ~ -1 + pi_r_k_t_minus_pi_r_t)
  
  model1_list[[paste(c("model1"),c(country_list[icountry]), sep = "_")]] <- reg1 
  cat(paste(c("Regression Results Model 1 for: "), c(country_list[icountry])))
  print_empty_line(html.output = FALSE)
  show(summ(reg1))
  print_empty_line(html.output = FALSE)
  print_empty_line(html.output = FALSE)

}
```

## Model 2

```{r}
model2_list <- list()
for (icountry in 1:length(country_list)){
  # Model 2 
  pi_r_k_t    <- unlist(I(df_final[(country_list[icountry])]*(log(df_final$dp_bd))))
  pi_r_t      <- unlist(I(df_final[(country_list[icountry])]*log(df_final$dp)))
  reg2        <- lm(data = df_final,log(g_gva_bd_share) ~ -1 + pi_r_k_t + pi_r_t  )
  
  model2_list[[paste(c("model2"),c(country_list[icountry]), sep = "_")]] <- reg2 
  print(paste(c("Regression Results Model 2 for: "), c(country_list[icountry])))
  show(summ(reg2))
}
```

## Model Parameter \(\eta^{c}\)

```{r}
eta_c <- list()

for (icountry in 1:length(country_list)){
  eta_c[[paste(c("model1"),c(country_list[icountry]), sep = "_")]] <- (1 - as.numeric(unlist(model1_list[[icountry]][1])))
  cat(paste("The Parameter eta_c for", country_list[icountry],"is", eta_c[icountry],sep =" "), sep = "\n\n")
}
```

