---
title: "Unemployment Regression"
author: "P Riehle"
date: "13 8 2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

# Preface

make sure the following packages are installed: package_list \<-
c("tidyverse", "OECD")

## check if needed packages are installed

```{r, warning= FALSE}

  libraries = c("tidyverse", "OECD", "tseries","CARS")

  junk = lapply(libraries, function(x) if (!(x %in% installed.packages())) {
    install.packages(x)
  })
  junk = lapply(libraries, library, quietly = TRUE, character.only = TRUE)

```

# Data Part:

## Definition of the needed input data

1:  Unemployment benefits average data: Public unemployment expenditure
    in percentage of the GDP 
2:  GDP 
3:  Number of unemployed persons 
4:  Annual average wage
5:  CPI

## Data Function Part

In this part of the code the functin is defined. The function
automatically downloads and prepares the dataset for the above defined
variables.

The input of the function is the corresponding country code of the OECD
(example: Germany = "DEU") One can find a list of the countries at:
(<https://www.oecd-ilibrary.org/docserver/9789264243439-8-en.pdf?expires=1628938923&id=id&accname=guest&checksum=82341B7046AA2F236762BE86993C53C7>)

```{r}
generate_dataset_benefits_reg <- function(country){
# Get all the data Ids from the OECD
dsets                             <- get_datasets()

### III. Search for the datasets

# 1.:  Unemployment benefits average data: 
#     Public unemployment expenditure in percentage of the GDP (SOCX_AGG)

# get the id
string                            <- search_dataset("Social Expenditure - Aggregated data", dsets)

#get the structure of the data
structure                         <- get_data_structure(string[1])

# get the data frame

# define a filter list based on the structure
filter_list                       <- list("10","7","0","0","PCT_GDP",country)
# extract the dataset
df_SOCX_AGG                       <- get_dataset("SOCX_AGG",filter = filter_list) 
# delete non necessary columns
df_SOCX_AGG                       <- df_SOCX_AGG[,-c(1:5,7,8,9)]
colnames(df_SOCX_AGG)[c(1:3)]     <- c("country","time","unemp_exp_pct_gdp")

# 2:  GDP 
string                            <- search_dataset("GDP",dsets)
structure                         <- get_data_structure(string[2,1])
filter_list                       <- list(country,"B1_GA","C")
df_SNA_TABEL1                     <- get_dataset(string[2,1], filter = filter_list)
df_SNA_TABEL1                     <- df_SNA_TABEL1[,-c(2:6,9)]
df_SNA_TABEL1[,3]                 <- df_SNA_TABEL1[,3] *1000000
colnames(df_SNA_TABEL1)[c(1:3)]   <- c("country","time","gdp_cp")


# 3:  Number of unemployed persons
string                            <- search_dataset("ALFS", dsets) #ALFS_SUMTAB/DEU.YGTT06L1_ST.A
structure                         <- get_data_structure(string[2,1])
filter_list                       <- list(country,"YGTT06L1_ST","A")
df_ALFS_SUMTAB                    <- get_dataset("ALFS_SUMTAB",filter = filter_list) 
df_ALFS_SUMTAB                    <-  df_ALFS_SUMTAB[,-c(2:6,9)]
df_ALFS_SUMTAB[,3]                <- df_ALFS_SUMTAB[,3]*1000
colnames(df_ALFS_SUMTAB)[c(1:3)]  <- c("country", "time", "unemp_pers")

# 4: Annual average wage
string                            <- search_dataset("WAGE", dsets) #AV_AN_WAGE/DEU.CPNCU
structure                         <- get_data_structure(string[3,1])
filter_list                       <- c(country,"CPNCU")
df_AV_AN_WAGE                     <- get_dataset(string[3,1],filter = filter_list) 
df_AV_AN_WAGE                     <- df_AV_AN_WAGE[,-c(2:5)]
colnames(df_AV_AN_WAGE)[c(1:3)]   <- c("country","time","avg_w_cp")

# 5: CPI 


filter_list                       <- c(country,"CPALTT01","IXOB","A")
df_CPI_base_15                    <- get_dataset("PRICES_CPI", filter = filter_list)
df_CPI_base_15                    <- df_CPI_base_15[, -c(2:8)]
colnames(df_CPI_base_15)[c(1:3)]  <- c("country","time","cpi_base_15")
### Merge the data frames 

# merge two data frames by ID
df_final                          <- list(df_SNA_TABEL1,df_SOCX_AGG, df_ALFS_SUMTAB,df_AV_AN_WAGE,df_CPI_base_15) %>%                                                reduce(left_join, by = 
                                     c("country","time"))
df_final                          <- df_final %>% drop_na()

# calculations:
# 1. average benefit
df_final$avg_ben                  <- unname(unlist(df_final[,3])*unlist(df_final[,4])/100/unlist(df_final[,5]))

# 2. real GDP
df_final$r_gdp                    <- df_final$gdp_cp/(df_final$cpi_base_15/100)
# 3. real average benefit 
df_final$r_avg_ben                <- df_final$avg_ben/(df_final$cpi_base_15/100)
# 4. real average wage
df_final$r_avg_w                  <- df_final$avg_w_cp/(df_final$cpi_base_15/100)  

# lag variables

df_final$r_avg_w_lag              <- lag(df_final$r_avg_w,1) 
df_final$r_avg_ben_lag            <- lag(df_final$r_avg_ben,1)
return(df_final)  
}
```



## Summarise the Dataset

```{r}
countries_list                    <-c("DEU","ITA","POL") 
```



```{r}
for (i in 1:length(countries_list)){
df                                <- generate_dataset_benefits_reg(countries_list[i]) 
show(summary(df))
}
```
## Visualisation:

### GDP at Current Prices:
```{r}
for (i in 1:length(countries_list)){
  df                                <- generate_dataset_benefits_reg(countries_list[i])
  plot(df$time,df$r_gdp/10^12, ylab = "Real GDP in Billion (base=2015)", xlab = "YEAR", type = "l" )
}
```
### Unemployed Persons in Million:

```{r}
for (i in 1:length(countries_list)){
  df                                <- generate_dataset_benefits_reg(countries_list[i])
  plot(df$time,df$unemp_pers/10^6, ylab = "Unemployed Persons in Million", xlab = "YEAR", type = "l" )
}
```
### Average Wage at Current Prices:

```{r}
for (i in 1:length(countries_list)){
  df                                <- generate_dataset_benefits_reg(countries_list[i])
  plot(df$time,df$r_avg_w, ylab = "Real Average Wage (base=2015)", xlab = "YEAR", type = "l" )
}
```

### Average Unemployment Benefit per Person:

$AV\_UNEMP\_BEN_t = \frac{GDP_t^{cp}*\frac{\%UNEMP\_EXP_t}{100}}{UNEMP\_PERS_t}$

```{r}
for (i in 1:length(countries_list)){
  df                                <- generate_dataset_benefits_reg(countries_list[i])
  plot(df$time,df$r_avg_ben, ylab = "Real Average Unemployment Benefit (base=2015)", xlab = "YEAR", type = "l" )
}
```

# Regression Part


The previous generated data set is used to test the following expression:

$B_t = \rho^{b^{1/4}}*B_{t-1}+ (1-\rho^{b^{1/4}})*\zeta*W_{t-1}$

```{r}

df = data.frame()
for (i in 1:length(countries_list)){
  temp <-  generate_dataset_benefits_reg(countries_list[i])
  df <- rbind(df, temp)
}

### Create dummies

df$Germany                        <- recode(df$country, "DEU"=1, "ITA"=0, "POL"=0)
df$Italy                          <- recode(df$country, "ITA"=1, "DEU"=0, "POL"=0)
df$Poland                         <- recode(df$country, "DEU"=0, "ITA"=0, "POL"=1)

model                             <- lm( r_avg_ben ~ -1  + I(Poland*r_avg_ben_lag)+ I(Poland*r_avg_w_lag) + I(Germany*r_avg_ben_lag) + I(Germany*r_avg_w_lag) + I(Italy*r_avg_ben_lag) + I(Italy*r_avg_w_lag),data = df)
summary(model)

adf.test(model$residuals)

plot(model$residuals)

```
